Computer Science House Constitution

### 2025-02-04 constitution.tex
Fix grammar and spelling issues

\asubsection{Leave of Absence Return}
A member may return from a leave of absence whichever they choose to.
When a member wishes to return, they must in writing notify a staff member of ResLife, excluding student employees, to end their leave of absence.

@@

\asubsection{Leave of Absence for Executive Board Member}
The duties and responsibilities of an E-Board member on leave are assumed using the process defined in \ref{Appointment of an Interim Director} until the member returns from their leave.
If the member returns before the end of the Standard Operation Session in which they started their leave, they may assume their position and the interim director is removed. % someone gets their position back if they come back during the year for which they were elected
If any point the member's leave is determined by E-Board to be detrimental to be operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.

@@

\asubsubsection{Responsibilities of the Executive Board}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH, if they are a Voting Member
	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
	\item To report pertinent information to members at the following House Meeting
	\item To maintain records of the goals defined by each previous E-Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects as defined in \ref{Expectations of Active Members}
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
	\item To publish a document at the end of each semester to all members stating CSH's accomplishments of that semester
	      %\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
	      %The constitution should remain up to date with current practices.
\end{enumerate}

@@

\asection{Anti-Discrimination Clause}
This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity and gender expression, religion, age marital state, national origin, disability or veteran status.
This policy will include but is not limited to, recruiting, membership, organization activities or opportunities to hold or run for club office.

>>>>

\asubsection{Leave of Absence Return}
A member may return from a leave of absence whenever they choose to.
When a member wishes to return, they must in writing notify a staff member of ResLife, excluding student employees, to end their leave of absence.

@@

\asubsection{Leave of Absence for Executive Board Member}
The duties and responsibilities of an E-Board member on leave are assumed using the process defined in \ref{Appointment of an Interim Director} until the member returns from their leave.
If the member returns before the end of the Standard Operation Session in which they started their leave, they may assume their position and the interim director is removed. % someone gets their position back if they come back during the year for which they were elected
If any point the member's leave is determined by E-Board to be detrimental to the operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.

@@

\asubsubsection{Responsibilities of the Executive Board}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH, if they are a Voting Member
	\item To meet at least once per week during the Standard Operating Session to discuss and report the operations of CSH
	\item To report pertinent information to members at the following House Meeting
	\item To maintain records of the goals defined by each previous E-Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects as defined in \ref{Expectations of Active Members}
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
	\item To publish a document at the end of each semester to all members stating CSH's accomplishments of that semester
	      %\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
	      %The constitution should remain up to date with current practices.
\end{enumerate}

@@

\asection{Anti-Discrimination Clause}
This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity, gender expression, religion, age, marital status, national origin, disability, or veteran status.
This policy will include but is not limited to, recruiting, membership, organization activities or opportunities to hold or run for club office.
